Usage metrics

### 2020-12-16 analysis/usage.Rmd
Tableof eval variants

@@

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", sites_per_package$n),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n)),
  r("max call sites", max_packages),
)
```

@@

And now, by `eval` variant:

```{r exercised-call-site-per-variant}

static_eval <- P %>% filter(call_fun_name == "eval") %>% nrow()
static_evalq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
static_eval.parent <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
static_local <- P %>% filter(call_fun_name == "local") %>% nrow()

r("static eval", static_eval)
r("static evalq", static_evalq)
r("static eval parent", static_eval.parent)
r("static local", static_local)

r("triggered eval", trig_eval)
r("triggered evalq", trig_evalq)
r("triggered eval parent", trig_eval.parent)
r("triggered local", trig_local)

r("eval percent call site", ratio(trig_eval, static_eval))
r("evalq percent call site", ratio(trig_evalq, static_evalq))
r("eval parent percent call site", ratio(trig_eval.parent, static_eval.parent))
r("local percent call site", ratio(trig_local, static_local))
```

>>>>

```{r exercised-call-site-per-variant}
static_eval <- P %>% filter(call_fun_name == "eval") %>% nrow()
static_evalq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
static_eval.parent <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
static_local <- P %>% filter(call_fun_name == "local") %>% nrow()

overview_table(
  r("StaticEval", static_eval),
  r("StaticEvalq", static_evalq),
  r("StaticEvalParent", static_eval.parent),
  r("StaticLocal", static_local),
  r("TriggeredEval", trig_eval),
  r("TriggeredEvalq", trig_evalq),
  r("Triggeredvalparent", trig_eval.parent),
  r("Triggeredlocal", trig_local),
  r("Triggeredevalpercent", ratio(trig_eval, static_eval)),
  r("Triggeredevalqpercent", ratio(trig_evalq, static_evalq)),
  r("Triggeredevalqpercent", ratio(trig_eval.parent, static_eval.parent)),
  r("Localevalqpercent", ratio(trig_local, static_local))
) -> TBL
```

@@

TBL <- overview_table(
  # Sites triggered over the whole corpus:
  r("nb eval call sites", sites),
  # How many packages in the corpus have a single triggered call site:
  r("nb one call site", sites_per_package %>% filter(n == 1)),
  r("at least one call site", nrow(sites_per_package)),
  r("packages no calls to eval", corpus_size - nrow(sites_per_package)),
  r("nb median call sites", median(sites_per_package$n)),
  r("max call sites", max_packages),
)
```

@@
